Running the MSE

### 2020-09-29 README.Rmd
added dynamics.r, added depleteSAU, and improved the conditioning code, though still more to do.

ctrl <- checkresdir(resdir)
runname <- ctrl$runlabel
zone1 <- readzonefile(resdir,ctrl$zonefile)
glb <- zone1$globals     # glb without the movement matrix
constants <- readdatafile(glb$numpop,resdir,ctrl$datafile)

>>>>

ctrl <- checkctrldat(resdir)
runname <- ctrl$runlabel
zone1 <- readzonefile(resdir,ctrl$zonefile)
glb <- zone1$globals     # glb without the movement matrix
constants <- readdatafile(glb$numpop,resdir,ctrl$datafile)

### 2020-09-29 data-raw/Running_aMSE.Rmd
added dynamics.r, added depleteSAU, and improved the conditioning code, though still more to do.

ctrl <- checkresdir(resdir)
zone1 <- readzonefile(resdir,ctrl$zonefile)
glb <- zone1$globals
constants <- readdatafile(glb$numpop,resdir,ctrl$datafile)

>>>>

ctrl <- checkctrldat(resdir)
zone1 <- readzonefile(resdir,ctrl$zonefile)
glb <- zone1$globals
constants <- readdatafile(glb$numpop,resdir,ctrl$datafile)
